Trajectories

### 2022-12-02 index.qmd
Fix colours in report

predicted_dfs %>% 
    ungroup() %>% 
    select(.prediction, .draw) %>% 
    count(.draw, .prediction) %>%
    group_by(.draw) %>% 
    mutate(
        prop = n/sum(n),
        .prediction = factor(
            .prediction,
            levels = levels(df$response), 
            ordered = TRUE
        )
    ) %>% 
    ggplot(aes(.draw, prop, fill = .prediction, colour = .prediction)) +
    geom_line(aes(group = .prediction)) +
    geom_rect(
        data = observed_prop,
        aes(xmin = 0, xmax = max(predicted_dfs$.draw),
            ymin = prop-0.025, ymax = prop+0.025,
            colour = .prediction, fill = .prediction),
        alpha = 0.25, colour = NA, inherit.aes = FALSE
    ) +
    # geom_segment(
    #     data = observed_prop,
    #     aes(x = -Inf, xend = Inf, y = prop, yend = prop,
    #         colour = .prediction),
    #     size = 1, inherit.aes = FALSE
    # ) +
    labs(
        x = "Iteration",
        y = "Proportion of responses",
        colour = "Response",
        fill = "Response"
    ) +
    scale_colour_d3() +
    scale_fill_d3() +
    scale_x_continuous(labels = label_number(big.mark = ","), 
                       breaks = seq(0, max(predicted_dfs$.draw), 100)) +
    scale_y_continuous(labels = percent, breaks = seq(0, 1, 0.05)) +
    theme(
        legend.position = "top",
        panel.grid = element_blank()
    )

>>>>

predicted_dfs %>% 
    ungroup() %>% 
    select(.prediction, .draw) %>% 
    count(.draw, .prediction) %>%
    group_by(.draw) %>% 
    mutate(
        prop = n/sum(n),
        .prediction = factor(
            .prediction,
            levels = levels(df$response), 
            ordered = TRUE
        )
    ) %>% 
    ggplot(aes(.draw, prop, fill = .prediction, colour = .prediction)) +
    geom_line(aes(group = .prediction)) +
    geom_rect(
        data = observed_prop,
        aes(xmin = 0, xmax = max(predicted_dfs$.draw),
            ymin = prop-0.025, ymax = prop+0.025,
            colour = .prediction, fill = .prediction),
        alpha = 0.25, colour = NA, inherit.aes = FALSE
    ) +
    # geom_segment(
    #     data = observed_prop,
    #     aes(x = -Inf, xend = Inf, y = prop, yend = prop,
    #         colour = .prediction),
    #     size = 1, inherit.aes = FALSE
    # ) +
    labs(
        x = "Iteration",
        y = "Proportion of responses",
        colour = "Response",
        fill = "Response"
    ) +
    scale_colour_manual(values = clrs[c(1, 3, 5)]) +
    scale_fill_manual(values = clrs[c(1, 3, 5)]) +
    scale_x_continuous(labels = label_number(big.mark = ","), 
                       breaks = seq(0, max(predicted_dfs$.draw), 100)) +
    scale_y_continuous(labels = percent, breaks = seq(0, 1, 0.05)) +
    theme(
        legend.position = "top",
        panel.grid = element_blank()
    )
